The sweet spot for local polygenic adaptation: a case study motivated by stickleback

### 2018-09-13 Stickleback_Paper.tex
Captions and Cleanup

\paragraph{Using SLiM's TreeSeq}
This case study involves analyzing large simulations which model populations under the influence of selection. 
To fully understand the origins of adaptive variants, calculate statistics, and avoid the computationally expensive task of 
simulating neutral mutations, we have used SLiM's \emph{treeSeq} feature to track the genealogical history of all samples throughout the simulation. 
This feature outputs a compact representation the genomic outcome of every meiosis relevant to tracked samples (Often thought of as the ARG).
\jgg{maybe the below should be in descriptive statistics}
To understand recomposition of the freshwater haplotype in the new lakes through selection, 
we were able to classify each adaptive variant, in each genome in the population at the generation at time of adaptation,
as deriving from one of four origins:
(1) Migrants, brought in from a migrant after the introduction of the new lakes 
(2) Pre-existing, passed down from an individual in the original generation of the new lakes, 
however, not defined to be an adaptive variant in the original lakes
(3) Captured, Pre-existing, passed down from an individual in the original generation of the new lakes, 
and defined to be adaptive in the original lakes
(4) De novo, mutated and propagated from an individual existing in the introduced lakes population, after introduction.

@@

\paragraph*{Speed of adaptation}
Increasing migration rate strongly decreased the time until freshwater habitats could adapt,
both in the old and new sets of lakes.
The different rates of introduction of effect alleles is clearly seen in the traces
of trait values against time (e.g., Figure \ref{fig:phenotype_ts2}).
As shown in Figure \ref{fig:TimeToAdaptation}, at the lowest migration rate 
it took over $20,000$ generations for the mean trait value across introduced lakes to 
get to within 0.5 of the original lakes value.
At $m = 1.0$, we saw the introduced population adapt in just 32 generations. 
This rate of adaptation follows what we've observed in natural populations of Threespine stickleback.
At the highest migration rate, $m = 100$, all individuals were unable to locally adapt.

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Migration load and genetic variation}

%FIGURES THAT SHOW THIS:
%- Phenotype Distribution
\begin{figure}[h!tb]
	\begin{center}
  		\includegraphics[width=1.0\linewidth]{semi_final_plots/PhenoDist_semi_final.png}
  		\caption{Distribution of mean phenotype throughout simulation runs at separate migration rate ($M$) parameter values, for each population.
		The dashed pink line (Pheno = +10) is the optimum phenotype any individual in the marine environment.
		In contrast the purple line at (Pheno = -10) represents the optimum for any individual in the freshwater environment. 
		All individuals at generation 0 (beginning of the simulation) 
		}
  		\label{fig:MeanPhenotype}
	\end{center}
\end{figure}

%GENERAL

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Realized genomic architecture}

\begin{figure}[h!tb]
	\begin{center}
  		\includegraphics[width=1.0\linewidth]{semi_final_plots/Haplo_semi_final.png}
  		\caption{
			Finish when plot is finalized. 
		}
  		\label{fig:MeanPhenotype}
	\end{center}
\end{figure}

@@

\begin{figure}
	\begin{center}
  		\includegraphics[width=0.7\linewidth]{semi_final_plots/TP_SP_semi_final.png}
  		\caption{ 
		%SP - suppose you have an Fst Peak, how likely is it that that region is causal. 
		Statistical Power and False Positives as a function of $F_{st}$ threshold. 
		Statistical Power is the likelihood that a SNP will be predicted to have an effect on phenotype when there is an effect to be detected (?).
		False Positives give us the ratio of SNPs that effect phenotype to total SNPs greater than the $F_{st}$ threshold.
        TODO: x-axis label ($F_{ST}$).
		}
  		\label{fig:Power_FP}
	\end{center}
\end{figure}

@@

\begin{figure}
	\begin{center}
  		\includegraphics[width=0.7\linewidth]{semi_final_plots/OriginRatio.png}
  		\caption{ 
		Ratio of Origins of adaptive alleles in all genomes at time of local adaptation for different values of $m$
		}
  		\label{fig:Origin}
	\end{center}
\end{figure}

>>>>

\paragraph{TreeSeq}
This case study involves analyzing large simulations which model populations under the influence of selection. 
To fully understand the origins of adaptive variants, calculate statistics, and avoid the computationally expensive task of 
simulating neutral mutations, we have used SLiM's \emph{treeSeq} feature to track the genealogical history of all samples throughout the simulation. 
This feature outputs a compact representation the genomic outcome of every meiosis relevant to tracked samples (Often thought of as the ARG).
\jgg{maybe the below should be in descriptive statistics}
To understand recomposition of the freshwater haplotype in the new lakes through selection, 
we were able to classify each adaptive variant, in each genome in the population at the generation at time of adaptation,
as deriving from one of four origins:
(1) Migrants, brought in from a migrant after the introduction of the new lakes 
(2) Pre-existing, passed down from an individual in the original generation of the new lakes, 
however, not defined to be an adaptive variant in the original lakes
(3) Captured, Pre-existing, passed down from an individual in the original generation of the new lakes, 
and defined to be adaptive in the original lakes
(4) De novo, mutated and propagated from an individual existing in the introduced lakes population, after introduction.

@@

\paragraph*{Speed of adaptation}
Increasing migration rate strongly decreased the time until freshwater habitats could adapt,
both in the old and new sets of lakes.
The different rates of introduction of effect alleles is clearly seen in the traces
of trait values against time (e.g., Figure \ref{fig:phenotype_ts2}).
As shown in Figure \ref{fig:TimeToAdaptation}, at the lowest migration rate 
it took over $20,000$ generations for the mean trait value across introduced lakes to 
get to within 0.5 of the original lakes value.
At $m = 1.0$, we saw the introduced population adapt in just $32$ generations. 
This rate of adaptation follows what we've observed in natural populations of Threespine stickleback.
At the highest migration rate, $m = 100$, all individuals were unable to locally adapt.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% I'M HERE

@@

\subsection*{Migration load and genetic variation}

\begin{figure}[h!tb]
	\begin{center}
  		\includegraphics[width=0.6\linewidth]{semi_final_plots/PhenoDist_semi_final.png}
  		\caption{Distribution of mean phenotype throughout simulation runs at separate migration rate ($M$) parameter values, for each population.
		The dashed pink line (Pheno = +10) is the optimum phenotype any individual in the marine environment.
		In contrast the purple line at (Pheno = -10) represents the optimum for any individual in the freshwater environment. 
		All individuals at generation 0 (beginning of the simulation) 
		}
  		\label{fig:MeanPhenotype}
	\end{center}
\end{figure}

@@

\subsection*{Realized genomic architecture}

\begin{figure}[h!tb]
	\begin{center}
  		\includegraphics[width=1.0\linewidth]{semi_final_plots/Haplo_semi_final.png}
  		\caption{
			Phenotypes (\textbf{Top}) (effect size and mutation type) and haplotypes \textbf{(Botton)} as a function of spatial position of the individual 
			possessing the genome. The phenotype of each haplotype is, by definition, the sum of the 
			effect sizes of each mutation in the genome. 
		}
  		\label{fig:MeanPhenotype}
	\end{center}
\end{figure}

@@

\begin{figure}
	\begin{center}
  		\includegraphics[width=0.7\linewidth]{semi_final_plots/TP_SP_semi_final.png}
  		\caption{ 
		Statistical Power and False Positives as a function of $F_{st}$ threshold. 
		Statistical Power is the likelihood that a SNP will be predicted to have an effect on phenotype when there is an effect to be detected (?).
		False Positives give us the ratio of SNPs that effect phenotype to total SNPs greater than the $F_{st}$ threshold.
        		TODO: x-axis label ($F_{ST}$).
		}
  		\label{fig:Power_FP}
	\end{center}
\end{figure}

@@

\begin{figure}
	\begin{center}
  		\includegraphics[width=0.7\linewidth]{semi_final_plots/OriginRatio.png}
  		\caption{ 
		Origin ratio of adaptive alleles in all genomes at time of local adaptation for different values of $m$
		For all alleles at a frequency $> 0.5$ in any one of the new lakes individuals at time of adaptation, 
		we traced the origin of the segment of DNA back in time to classify them as 
		\textbf{(Blue)} Migrants, brought in from a migrant after the introduction of the new lakes 
		\textbf{(Orange)} Pre-existing, passed down from an individual in the original generation of the new lakes, 
		however, not defined to be an adaptive variant in the original lakes
		\textbf{(Green)} Captured, Pre-existing, passed down from an individual in the original generation of the new lakes, 
		and defined to be adaptive in the original lakes
		\textbf{(Red)} De novo, mutated and propagated from an individual existing in the introduced lakes population, after introduction. 
		}
  		\label{fig:Origin}
	\end{center}
\end{figure}
